### 2024-09-18 cognitive-bias.qmd
20240918 - copyediting

*Loss aversion bias* is the tendency to avoid losses rather than acquiring equivalent gains.
That is, loss aversion (similar to punishment sensitivity, as opposed to reward sensitivity) is the tendency to weigh losses (or punishment) more heavily than gains (or rewards).
Loss aversion is a key aspect of prospect theory [@Kahneman2011].
The loss aversion ratio indicates the extent to which a person weighs losses greater than gains, and for many people is between 1.5 to 2.5 [@Kahneman2011].
Loss aversion is different from [risk aversion](#sec-cognitiveBiasesRiskAversion).
Loss aversion is exemplified when teams play conservatively so as "not to lose" instead of "to win."
In fantasy football, loss aversion may lead managers to start or hold onto underperforming high drafted players for too long instead of starting a more promising player out of fear of losing potential value from their initial investment.

>>>>

*Loss aversion bias* is the tendency to avoid losses rather than acquiring equivalent gains.
That is, loss aversion (similar to punishment sensitivity, as opposed to reward sensitivity) is the tendency to weigh losses (or punishment) more heavily than gains (or rewards).
Loss aversion is a key aspect of prospect theory [@Kahneman2011].
The loss aversion ratio indicates the extent to which a person weighs losses greater than gains, and for many people is between 1.5 to 2.5 [@Kahneman2011].
Loss aversion is different from [risk aversion](#sec-cognitiveBiasesRiskAversion).
Loss aversion is exemplified when teams play conservatively so as "not to lose" instead of "to win."
In fantasy football, loss aversion may lead managers to start or hold onto players for too long who were highly drafted yet are underperforming instead of starting a more promising player out of fear of losing potential value from their initial investment.
